Process-based phenotypes: an application to the Cellular Phenotype Ontology

### 2011-11-23 trunk/paper/drinking.tex

A second kind of regulatory abnormalities is related to the {\em
  onset} of a process. With respect to a reference process, a
particular kind of process may be {\em delayed} ({\tt PATO:0000502})
or {\em premature} ({\tt PATO:0000694}). For example, {\em Delayed
  apoptosis} refers to an abnormality of the {\em Regulation of
  apoptosis} in which apoptosis is induced later than normal.  We use
the PATO quality {\em onset} ({\tt PATO:...}) and its children {\em
  delayed} and {\em premature} to define these types of regulatory
abnormality. Similarly, we use PATO's {\em offset ({\tt PATO:...})
  quality and its children to characterize regulatory abnormalities in
  which a process ends prematurely or too late.

>>>>

A second kind of regulatory abnormalities is related to the {\em
  onset} of a process. With respect to a reference process, a
particular kind of process may be {\em delayed} ({\tt PATO:0000502})
or {\em premature} ({\tt PATO:0000694}). For example, {\em Delayed
  apoptosis} refers to an abnormality of the {\em Regulation of
  apoptosis} in which apoptosis is induced later than normal.  We use
the PATO quality {\em onset} ({\tt PATO:...}) and its children {\em
  delayed} and {\em premature} to define these types of regulatory
abnormality. Similarly, we use PATO's {\em offset} ({\tt PATO:...})
  quality and its children to characterize regulatory abnormalities in
  which a process ends prematurely or too late.
